---
title: " API R projects"
author: "Maximilian Pfundstein, Annalena Erhard, Ruben Munoz"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true

vignette: >
  %\VignetteIndexEntry{API R projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)

```


```{r echo=FALSE, fig.show='hide'}

library(httr)
library(jsonlite)
library(plyr)

# Basic Data
base = "http://api.kolada.se/"
api_version = "v2/"

#' Fetch Municipalities
#'
#' @return Returns a data.frame containing all municipalities.
#' @export
#'
fetchMunicipalities = function() {
  endpoint = "municipality"
  webCall = paste(base, api_version, endpoint, sep="")
  
  # Execution
  response = GET(webCall)
  
  # Check Server Response
  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")
  
  # Deserialization
  result = fromJSON(content(response, "text", encoding = "utf-8"), flatten = TRUE)
  
  return(as.data.frame(result))
}

#' Fetch KPIs
#'
#' @return Returns a data.frame containing all KPIs with their id and description.
#' @export
#'
fetchKpis = function() {
  endpoint = "kpi_groups"
  webCall = paste(base, api_version, endpoint, sep="")
  
  # Execution
  response = GET(webCall)
  
  # Deserialization
  result = fromJSON(content(response, "text", encoding = "utf-8"), flatten = FALSE)
  
  # Check Server Response
  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")
  
  # Prepare Data Frames
  kpi.group.data.frame = as.data.frame(result)
  kpi.data.frame = data.frame(member_id = integer(), member_title = character())
  
  # Extract required data
  for (i in 1:nrow(kpi.group.data.frame)) {
    group_kpi = kpi.group.data.frame[i, 3][[1]]
    kpi.data.frame = rbind(kpi.data.frame, group_kpi)
  }
  return(kpi.data.frame)
}

#' Fetch By Municipality
#'
#' @param municipality Id of the municipality.
#' @param year The year as integer.
#'
#' @return Returns a data.frame containing all KPIs belonging to the municipality in the given year.
#' @export
#'
fetchByMunicipality = function(municipality, year){
  #http://api.kolada.se/v2/data/municipality/1860/year/2009
  
  if (length(municipality) != 1 | !is.numeric(municipality)) stop("municipality parameter must be a numeric scalar.")
  if (!is.numeric(year) | !is.vector(year)) stop("year must be a numeric vector")
  
  endpoint = "data/municipality/"
  
  webCall = paste(base, api_version, endpoint, municipality, "/year/", sep="")
  
  for (i in 1:length(year)) {
    webCall = paste(webCall, year[i], sep = "")
    if (i != length(year)) webCall = paste(webCall, ",", sep="")
  }
  
  # Execution
  response = GET(webCall)
  
  # Check Server Response
  print(response)
  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")
  
  # Deserialization
  result = fromJSON(content(response, "text"), flatten = TRUE)
  return(as.data.frame(result))
}

#' Fetch By KPI
#'
#' @param kpi Id of the KPIs as a list.
#' @param municipality Id of the municipality.
#' @param year The years to fetch as a vector
#'
#' @return Returns a data.frame containing the requested data
#' @export
#'
fetchByKpi = function(kpi, municipality , year = c()) {
  
  if (any(grepl("[,]", kpi) == TRUE)) stop("character ',' is not allowed for kpis")
  if (length(kpi) == 0) stop("kpi contains no entries")
  if (!is.list(kpi)) stop("kpi must be a list")
  if (!is.vector(year)) stop("year is not a vector")
  
  endpoint = "data/kpi/"

  webCall = paste(base, api_version, endpoint, sep="")
  
  for (i in 1:length(kpi)) {
    webCall = paste(webCall, kpi[i], sep="")
    if (i != length(kpi)) webCall = paste(webCall, ",", sep="")
  }
  
  webCall = paste (webCall, "/municipality/", municipality, sep="")

  if (length(year) > 0) {
    webCall = paste(webCall, "/year/", sep="")
    
    for (j in 1:length(year)) {
      webCall = paste(webCall, year[j], sep="")
      if (j != length(year)) webCall = paste(webCall, ",", sep="")
    }
  }
  
  # Execution
  response = GET(webCall)

  # Check Server Response
  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")
  
  # Deserialization
  result = fromJSON(content(response, "text"), flatten = TRUE)
  if (result["count"] == 0) return(data.frame())
  return(as.data.frame(result))
}

```

### fetchMunicipalities
A method call that gives back a dataset with details about municipalities.

```{r, fig.show='hold'}

head(fetchMunicipalities())
```


### fetchKpis

A method call that gives back a dataset with all member id's and the associated description.

```{r, fig.show='hold'}

head(fetchKpis())

```

### fetchByMunicipality

A method call that returns a dataset with all values for the prespecified municipality and year.

```{r, fig.show='hold'}

head(fetchByMunicipality(1440, c(2012, 2013)))

```



### fetchByKpi

A method call that gives back a dataset with all values for the prespecified kpis, municipality and year.
In this example the kpi's "N00914" and "U00405" of the municipailty 1440 and year 2010, 2011 and 2012 are fetched. The method returns a data frame.

```{r, fig.show='hold'}

head(fetchByKpi(list("N00914", "U00405"), 1440, c(2010, 2011, 2012)))
```



### Example API
http://api.kolada.se/v2/data/municipality/1860/year/2009 



