---
title: " API R projects"
author: "Maximilian Pfundstein, Annalena Erhard, Ruben Munoz"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true

vignette: >
  %\VignetteIndexEntry{API R projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)

```


```{r echo=FALSE, fig.show='hide'}

library(httr)

library(jsonlite)

library(plyr)



# Basic Data

base = "http://api.kolada.se/"

api_version = "v2/"



#' Fetch Municipalities

#'

#' @return Returns a data.frame containing all municipalities.

#' @export

#'

#' @examples fetchMunicipalities()

fetchMunicipalities = function() {

  endpoint = "municipality"

  webCall = paste(base, api_version, endpoint, sep="")

  

  # Execution

  response = GET(webCall)

  

  # Check Server Response

  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")

  

  # Deserialization

  result = fromJSON(content(response, "text", encoding = "utf-8"), flatten = TRUE)

  

  return(as.data.frame(result))

}



#' Fetch KPIs

#'

#' @return Returns a data.frame containing all KPIs with their id and description.

#' @export

#'

#' @examples fetchKpis()

fetchKpis = function() {

  endpoint = "kpi_groups"

  webCall = paste(base, api_version, endpoint, sep="")

  

  # Execution

  response = GET(webCall)

  

  # Deserialization

  result = fromJSON(content(response, "text", encoding = "utf-8"), flatten = FALSE)

  

  # Check Server Response

  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")

  

  # Prepare Data Frames

  kpi.group.data.frame = as.data.frame(result)

  kpi.data.frame = data.frame(member_id = integer(), member_title = character())

  

  # Extract required data

  for (i in 1:nrow(kpi.group.data.frame)) {

    group_kpi = kpi.group.data.frame[i, 3][[1]]

    kpi.data.frame = rbind(kpi.data.frame, group_kpi)

  }

  return(kpi.data.frame)

}



#' Fetch By Municipality

#'

#' @param municipality Id of the municipality.

#' @param year The year as integer.

#'

#' @return Returns a data.frame containing all KPIs belonging to the municipality in the given year.

#' @export

#'

#' @examples fetchByMunicipality(1440, 2012)

fetchByMunicipality = function(municipality, year){

  #http://api.kolada.se/v2/data/municipality/1860/year/2009

  

  endpoint = "data/municipality/"

  

  webCall = paste(base, api_version, endpoint, municipality, "/year/", year, sep="")

  

  # Execution

  response = GET(webCall)

  

  # Check Server Response

  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")

  

  # Deserialization

  result = fromJSON(content(response, "text"), flatten = TRUE)

  return(as.data.frame(result))

}



#' Fetch By KPI

#'

#' @param kpi Id of the KPIs as a list. Seperator is a ','.

#' @param municipality Id of the municipality.

#' @param year (optional) The year as integer.

#'

#' @return Returns a data.frame containing the

#' @export

#'

#' @examples fetchByKpi(list("N00914,U00405"), 1440, 2012)

fetchByKpi = function(kpi, municipality , year = 0) {



  endpoint = "data/kpi/"



  webCall = paste(base, api_version, endpoint, sep="")

  

  for (i in 1:length(kpi)) {

    webCall = paste(webCall, kpi[i], sep="")

    if (i != length(kpi)) webCall = paste(webCall, ",", sep="")

  }

  

  webCall = paste (webCall, "/municipality/", municipality, sep="")



  if (year > 0) webCall = paste(webCall, "/year/", year, sep="")

  

  # Execution

  response = GET(webCall)



  # Check Server Response

  if (response["status_code"] < 200 | response["status_code"] > 299) stop("HTTP Stauts code it not OK (not in range 200-299).")

  

  # Deserialization

  result = fromJSON(content(response, "text"), flatten = TRUE)

  if (result["count"] == 0) return(data.frame())

  return(as.data.frame(result))

}



a = fetchMunicipalities()

b = fetchKpis()

c = fetchByKpi(list("N00914,U00405"), 1440, 2012)

#d = fetchByMunicipality(1440)



```




## Introduction {.tabset}

This package uses R to connect to a web API. It uses a Shiny App, in which two seperately constructed plots can be compared with each other. For each of the plots the user can select municipalities KPI's and years. For every selection an API call is set to draw the data. 


## Usage Methods {.tabset .tabset-fade .tabset-pills}

```{r echo=TRUE, fig.show='hold'}
```


### fetchMunicipalities 

A method call that gives back a dataset with all municipalities, their count, id and value type.
```{r, fig.show='hold'}

fetchMunicipalities()

```



### fetchKpis

A method call that gives back a dataset with all member id's and the associated description.

```{r, fig.show='hold'}

b = fetchKpis()


```



### fetchKPI

A method call that gives back a dataset with all values for the prespecified kpis, municipality and year.

```{r, fig.show='hold'}

c = fetchByKpi(list("N00914,U00405"), 1440, 2012)


```
